R Notebook

### 2022-02-15 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd

# Lets create an statnet object from our edgelist
#####
#First we make the object. It will have no vertex or edge attributes
sourceEL_sn <- 
  network(as.matrix(source_netEdge[1:2], 
                    matrix.type = 'edgelist')
  )

@@

# Generating the EdgeList

##**round 1**
          # from "_netEdge" select "colNames" to be identified with "vertex.names"

@@

##**round 2**
            # code still selecting from "_netEdge", add "colNames"

colnames(temp)<- c("dnkIng")

@@

temp<- rbind(temp, source_netEdge[, c("dnkIng")])

@@

sourceEL_sn%v%"dnkName"<- 
  temp$dnkIng[match(sourceEL_sn%v%"vertex.names",
                    temp$dnkIng)]
      #####
            summary(sourceEL_sn)
dim(sourceEL_sn)

@@

 #**igraph** Generate Edgelist

@@

@@

@@

        # list the structure of smugCovIdx
    str(smugEL_ig )

@@

#     access vertex attributes
  head(smugEL_sn %v% "vertex.names")

>>>>

# Lets create an statnet object from our edgelist
#####
#First we make the object. It will have no vertex or edge attributes
sourceEL_sn <- 
  network(as.matrix(source_netEdge[1:2], 
                    matrix.type = 'edgelist',
                    loops=T,
                    hyper=T)
  )
print(sourceEL_sn)

@@

print(sourceEL_sn)

sourceEL_sn%v%"dnkName"<- sourceEL_sn%v%"vertex.names",source_netEdge$dnkName

print(sourceEL_sn)
# Generating the EdgeList
#####
##**round 1**
          # from "_netEdge" select "colNames" to be identified with "vertex.names"

@@

View(temp)
##**round 2**
            # code still selecting from "_netEdge", add "colNames"

 colnames(temp)<- c("dnkIng")
# View(temp)

@@

temp <- rbind(temp,source_netEdge[, c("dnkIng")])

View(temp)
#######

@@

sourceEL_sn%v%"dnkName"<- 
  temp$dnkName[match(sourceEL_sn%v%"vertex.names",
                    temp$dnkName)]
      #####
            summary(sourceEL_sn)
View(sourceEL_sn)

@@

#####
      #**igraph** Generate Edgelist
######

@@

            # list the structure of smugCovIdx
    str(smugEL_ig )
    str(smug_sn)

@@

```{r}

colnames(smugCovIdx)
#Lets make some network objects

smugCovIdx_igraph <- graph_from_data_frame(smugCovIdx)
print(smugCovIdx_igraph)

#Now let's create a statnet object

network_edgelist <- smugCovIdx

network_statnet <- network(as.matrix(network_edgelist[,c("dnkName")]), 
                             directed = FALSE, matrix.type = "edgelist")

  network_statnet%e%'dnkIng'  <- smugCovIdx$dnkIng
  network_statnet%e%'ingType' <- smugCovIdx$ingType

  network_statnet%v%'dnkName'<-
    as.character(smugCovIdx$dnkName[match(smugCovIdx,network_statnet%v%'vertex.names')])

print(network_statnet)

                                 #     access vertex attributes
  view(network_statnet%v% "vertex.names")
            # list the names of vertex attributes
  network::list.vertex.attributes(network_statnet)
            #  Generate a list the names of edge attributes
  network::list.edge.attributes(network_statnet)
            #   summarize numeric network attribute
  summary(network_statnet%v%"dnkName")

@@

@@

#     access vertex attributes
  view(smugEL_sn %v% "vertex.names")
